### 2021-06-29 background.tex
Review partially the background section

In this section we present information that is necessary to understand the remainder of this paper.
First, we introduce some background information about the use of \emph{sandbox} to protect access
to sensitive resources. After, we review the mining sandbox approach for detecting malicious
behavior in Android apps. Finally, we present some background information about
taint analysis.

\textbf{A Sandbox} is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps. Therefore, every month many Android apps are removed from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}. For security reasons, Google Play lists each app with the requested permission. However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}. Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product~\cite{DBLP:conf/soups/FeltHEHCW12}.

@@

\textbf{The Android Mining Sandbox} approach is a sandboxing technique that consists of mining rules from an Android app, and use these rules to ensure system security. The mining sandbox approach comprises of two steps. First, rules are mined and will compose the sandbox,
%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
through test generator tools, that identifies sensitive Android API, called during their execution. 
%\kn{This sentence seems to miss something "what" happens through test generation tools.}
These tools investigate program behavior through resource accesses realized by theses APIs. The second stage ensures that resources not accessed, or accessed differently than first stage, are not accessible by the apps. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

Automatically mining software resources or components, to infer behavior is not new, and has been discussed before. For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class. Ammons et al~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.

>>>>

In this section, we present information that is necessary to understand the remainder of this paper. First, we introduce some background information about the use of \emph{sandboxes} to protect access to sensitive resources. After, we review the mining sandbox approach for detecting malicious behavior in Android apps. Finally, we present some background information about taint analysis.

\textbf{A Sandbox} is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third-party software. Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the apps' publishment process. Therefore, every month administrators remove several Android apps from the Play Store because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}. For security reasons, Google Play lists each app with its requested permissions. However, many malicious apps usually ask for more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}. Those permissions are presented to the user during a new app's installation, since Android version 6, but most users are careless since they are only interested in the end product~\cite{DBLP:conf/soups/FeltHEHCW12}.

@@

\textbf{The Android Mining Sandbox} approach is a sandboxing technique that uses test generator tools to explore an Android app's dynamic behavior to define what sensitive resources are necessary to build the sandbox. And, we use this sandbox to ensure the app execution's security by restricting the resources that are allowed to use. In a first, exploratory phase, a practitioner uses test generator tools to execute a benign version of an app and record the set of sensitive APIs the app calls. Secondly, we define the sandbox based on the sensitive APIs mined in the first phase. This sandbox will ensure that malicious apps require only sensitive APIs, and if not, it will prohibit the malicious app's access.

Automatically mining software resources or components, to infer behavior is not new, and has been discussed before. For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class. Ammons et al.~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
